Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on conclusion

Overall, we reported \Fix{XX} bugs in this study. Of which, \Fix{YY}
were confirmed and \Fix{ZZ} were fixed by developers. Although more
work is necessary to reduce cost of manual analysis, we found that
both techniques we used are effective at finding bugs in the engines
used in the most popular we browsers used
today. Section~\ref{sec:lessons} elaborates on the lessons we learned
in this study. The result data, the infrastructure, and experimental
scripts we prepared to run this study are available upon request.

>>>>

Overall, we reported \totalBugsReported\ bugs in this study. Of which,
\totalBugsConfirmed\ were confirmed by developers and
\totalBugsConfirmed\ were fixed. Although more work is necessary to
reduce cost of manual analysis, we found that both techniques we used
are effective at finding bugs in
\js\ engines. Section~\ref{sec:lessons} elaborates on the lessons
learned from this study. The result data, infrastructure, and
experimental scripts we prepared to run this study are available upon
request. Future work includes mining test inputs from alternative
sources (\eg{}, bug trackers) and predicting likelihood of false
positives as to guide human effort on the most promising warnings
first.
